Community-conditioned language models for linguistic variation

### 2021-12-14 paper/paper1.tex
fix langid numbers

Using \texttt{langid.py} \citep{Lui2012}, we observe that a majority of the overall
messages are classified as English (94.6\% of the test set) and X of \num{510} communities %TODO
have more than half of their messages classified as English.
Given the small amount of non-English data, 
we decided that the bias introduced by attempting to filter message
by language outweighted the potential benefits.\footnote{
  See \cref{sec:ethics} for futher discussion.}

>>>>

Using \texttt{langid.py} \citep{Lui2012}, we observe that a majority of the overall
messages are classified as English (95\% of the test set) and 498 of \num{510} communities %TODO
have more than half of their messages classified as English.
Given the small amount of non-English data, 
we decided that the bias introduced by attempting to filter message
by language outweighted the potential benefits.\footnote{
  See \cref{sec:ethics} for futher discussion.}
